### 2022-04-12 README.Rmd
update badges

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://codecov.io/github/tidymodels/infer/?branch=main)

>>>>

[![R-CMD-check](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://codecov.io/github/tidymodels/infer/?branch=main)
